Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-10 Latex/journal_v1/V4/pr.tex
latex type journal finish system model and start algorithm part

Assume we have $S_1$, $S_2$ and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 + S_3$).
So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMtc). So each service request $s$ served by its corresponding slice.

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}^{e}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMtc is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{1,2\}$) application of service type 2 (URLLC) and 3 (mMtc) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_j,i)}^{u,r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){\beta}_{u(s_j,i)}^{k}\\
\mathcal{R}_{u(s_j,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{e,r} 
\end{split}
\end{equation}
Where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$, $j \in \{1,2\}$
and $\zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})$
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$C_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_j$.

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq1}.
\subsection{Power of O-RU and Fronthaul Capacity}
Let $P_r$ denote the power of transmitted signal from the $r^{th}$ RU to UEs served by it.
From \eqref{eq2}, we have,
\begin{equation}
P_r = \sum_{s=1}^{S}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \bold{p}_{r,u(s,i)}^{k} + \sigma_{q_{r(s,j)}}^2.
\end{equation}
Nevertheless, the rate of users on the fronthual link between DU and the $r^{th}$ RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}
C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \bold{p}_{r,u(s,i)}^{k} }{ \sigma_{q_{r}}^2})},
\end{equation}
where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is mapped to service $v$ or not .

\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
Here we assume the value of propagation delay and transmission is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

%In this system, the goal is to minimize the cost of the system.
Power of each O-RU is obtained as below
P_r =  \sum_{s=1}^{S} \sum_{i=1}^{U_v} \sum_{k=1}^{K_s}p_{r,u(s,i)}^{k}a_{u(s,i)} e^{k}_{r,u(s,i)}g_{u(s,i)}^r.
%The total power cost of O-RUs for transmitting data to UE is depicted as follow
%\begin{equation}
%P_{tot} = \sum_{r=1}^{R}P_r
%\end{equation}

@@

\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .

@@

Where,$z_d$ is shown that whether the $d^{th}$ DC is turned on or not and $\psi_d$ is a static cost when a DC is active.
  z_d =
    \begin{cases}
      1 & \sum_{s=1}^{S}y_{s,d} \geq 1 \\
      0 & \text{otherwise}
    \end{cases}       
In addition, $\phi_{s}$ is obtained from below

@@

Where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively. 
So the optimization problem is formulated as follow.

@@

\begin{subequations}

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G}, \boldsymbol{Y} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}} \ \\

@@

&\mathcal{R}_{u_{(s_1,i)}}^e \geq  a_{u(s_1,i)}\mathcal{R}_{min}^{s_1,e} \quad \forall s_1, \label{c13} \\
&\mathcal{R}_{u_{(s_2,i)}}^u \geq  a_{u(s_2,i)}\mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
& \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}}^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 

@@

& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
&a_{u(s,i)} \leq a_{u(s,i)}\sum_{r}g^r_{u(s,i)}  \quad \forall s,\forall i, \label{c17}  \\
& a_{u(s,i)}g^r_{u(s,i)} \leq a_{u(s,i)}g^r_{u(s,i)}\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)}  \quad \forall s,i , \label{c18} \\
& \phi_{tot}  \leq \phi_{max}, \label{c19} \\
 &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d} 
 \quad \forall d, \forall \mathfrak{z}\in \mathcal{E}; \label{c20}

@@

where $\boldsymbol{P} =[p_{u(s,i)}] \:\: \forall s , \forall i $, is the matrix of power for UEs, $\boldsymbol{A} =[a_{u(s,i)}] \:\: \forall s , \forall i $ denotes the binary variable for UE admission,
$\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice and $\boldsymbol{Y} =[y_{s,d}]  \:\: \forall s ,  \forall d $ is a binary variable shown whether
the physical DC is mapped to a VNFs of a slice or not.
Also, $\eta$ is weighted variable to value between the benefit and the cost term of objective function.

@@

Also \eqref{c13} and \eqref{c14} shows that the rate of each UE requesting eMBB and URLLC is more than a threshold, respectively.

@@

\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
\eqref{c17} and \eqref{c18} guarantee that if a UE in admitted by the system, O-RU and PRB is associated to it, respectively.

@@

Moreover, in \eqref{c20}  $\mathcal{E} = \{M,S,C, N\}$ and the constraint supports
that we have enough physical resources for VNFs of each slice.

\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

>>>>

Assume we have $S_1$, $S_2$ and $S_3$ different applications for the first, second and third service type, respectively ($S = S_1 + S_2 + S_3$).
So, we have $S$ preallocated slices serving these $S$ services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC) and $S_3$ slices for the third service type (mMTC). So each service request $s$ served by its corresponding slice.

@@

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} 
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated from follow
\begin{equation}\label{eq11}
\begin{split}
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} 
\end{split}
\end{equation}
Where $j \in \{1,2\}$. Also we have
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
\end{equation}
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable rate of each O-RU $r$ to UE $i$ in slice $s_j$.

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of O-RU and Fronthaul Capacity}
Let $P_r$ denote the power of transmitted signal from the $r^{th}$ O-RU to UEs served by it.
From \eqref{eq2}, we have,
\begin{equation}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_{r(s,j)}}^2.
\end{equation}
Since we have fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}
C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
\end{equation}
Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
Here we assume the value of propagation delay and transmission is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

\subsection{VNF Power}

@@

\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s}.

@@

Where, $\phi_{s}$ is obtained from below

@@

Moreover, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, O-CU and O-DU, respectively. 
The optimization problem is formulated as follow.

@@

\begin{subequations}\label{problem}

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}R_{u_{(s,k)}} \ \\

@@

&\mathcal{R}_{u_{(s_j,i)}} \geq \mathcal{R}_{min}^{s_j} \quad \forall s, j \in \{1,2,3\}, \label{c13} \\
%&\mathcal{R}_{u_{(s_2,i)}}^u \geq  \mathcal{R}_{min}^{s_2,u} \quad \forall s_2, \label{c14} \\
& C^r \leq C_{max}^r \quad \forall r, \label{c15}\\ 

@@

%& P_r\{E_1, E_2, E_3, E_4\} \leq \epsilon_s \quad \forall s_2, \label{c166}\\
& \sum_{r}g^r_{u(s,i)} \geq 1  \quad \forall s,\forall i, \label{c17}  \\
& \sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i , \label{c18} \\
& \phi_{tot}  \leq \phi_{max}, \label{c19} 

@@

where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.

@@

Also \eqref{c13} shows that the rate of each UE requesting eMBB, URLLC and mMTC is more than a threshold, respectively.

@@

%\eqref{c16} is a reliability condition that the delay in each layer should be less than threshold.
\eqref{c17} and \eqref{c18} guarantee that O-RU and PRB is associated to the UE, respectively.

@@

\section{Proposed Algorithm Scheme}
In this section, we first apply some simplifications to the system; Solving problem \eqref{problem} is complicated due to the fact that this problem is 
a non-convex problem and it is a 
mixed integer non-linear problem (MINLP) with a binary variable and an integer variable. 
In the following, we apply the simplifications to reformulate MINL parts and use iterative heuristic algorithm to solve the reformulated problem.
We solve this problem in two level iteratively until it converges; In the first level,
parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters and turn it to convex problem; Afterward we solve it by dual optimization problem.
In the second level, finding optimal O-RU association ($ \boldsymbol{G}$) is concerned with the fixed parameter of power, PRB allocation and number of VNFs.   
We repeat this procedure until the algorithm converges.
\subsection{Sub-Problem 1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.

As we mentioned before, by replacing $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ for $I_{r,u(s,i)}^{k}$ and lower bound $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ for  ${\mathcal{R}}_{u_{(s,i)}}$ is obtained by replacing with $I_{r,u(s,i)}^{k}$ $\bar{I}_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3} and make them concave.

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
To convexify \eqref{eq11}, we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.

Suppose UPF, O-CU and O-DU have the same processor 
\begin{lemma}
In problem \eqref{problem}, 
\end{lemma}
\bibliography{ref}
\end{document}
